%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COPYRRIGHT 2024, CHRISTOPHER FLIPPO, ALL RIGHTS RESERVED.
% christopher.allen.flippo@gmail.com
% https://github.com/Chris-AF
%
% COPYRIGHT APPLIES TO THE LATEX CODE SPECIFICALLY AND *NOT*
% TO THE TEXT OF THE HYMNS CONTAINED THEREIN.
%
% LICENSE: GPLv3
% LICENSE TEXT:
% https://www.gnu.org/licenses/gpl-3.0.en.html#license-text
% 
% LICENSE APPLIES TO THE LATEX CODE SPECIFICALLY AND *NOT*
% TO THE TEXT OF THE HYMNS CONTAINED THEREIN.
% 
% HYMN TEXT TAKEN FROM THE PARISH WEBSITE OF:
% The Orthodox Church of the Holy New Martyrs and Confessors of Russia
% OF THE EASTERN AMERICAN DIOCESE
% OF THE RUSSIAN ORTHODOX CHURCH OUTSIDE RUSSIA
%
% 364  Canterbury Turnpike
% Norwich, CT 06360
% (860) 822-1821
% admin@holynewmartyrs.org
% https://www.holynewmartyrs.org/tropariakontakia
%
% WITH THE PERMISSION OF:
% Fr. Stephen Kaznica
% (201) 398-5059
% frstephen@holynewmartyrs.org
%
% ON THE DATE:
% 15 OCT 2024
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}
\usepackage{blindtext}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage[object=vectorian]{pgfornament}

\usepackage[paperheight=5in,paperwidth=3.5in,margin=.1in]{geometry}
\linespread{0.4}

% ADAPTED FROM:
% https://tex.stackexchange.com/a/76555
%
% ON THE DATE:
% 15 OCT 2024
\newcommand{\sectionlinetwo}[2]{%
  \nointerlineskip \vspace{.5\baselineskip}\hspace{\fill}
  {\resizebox{0.9\linewidth}{1.3ex}
    {\pgfornament[color = #1]{#2}
    }}%
    \hspace{\fill}
    \par\nointerlineskip \vspace{.5\baselineskip}
  }

\begin{document}


\noindent
\centering
{
\color{red}
\tiny
\textbf{ORTHODOX CHRISTIAN WEEKDAY TROPARIA \& KONTAKIA}
}
\smallskip

\noindent
\centering
{
\footnotesize
\underline{\textbf{MONDAY}}
}
\smallskip

\noindent
\centering
{
\color{red}
\footnotesize
\textit{Commemoration of the Holy Angels}
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Troparion}
}

\noindent
\justifying
{
\scriptsize
Supreme Leaders of the Heavenly Hosts, we implore you that by your prayers you will encircle us, unworthy as we are, with the protection of the wings of your immaterial glory, and guard us who fall down I before you and fervently cry: Deliver us from dangers, for you are the commanders of the Powers above.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Kontakion}
}

\noindent
\justifying
{
\scriptsize
Supreme Leaders of God's armies and ministers of the divine glory, princes of the bodiless Angels and guides of men, ask what is good for us and great mercy, as Supreme Leaders of the Bodiless Hosts.
}
\medskip

\noindent
\centering
{
\footnotesize
\underline{\textbf{TUESDAY}}
}
\smallskip

\noindent
\centering
{
\color{red}
\footnotesize
\textit{Commemoration of St. John the Baptist}
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Troparion}
}

\noindent
\justifying
{
\scriptsize
The memory of the just is celebrated with hymns of praise, but the Lord's testimony is enough for thee, O Forerunner, for thou wast shown to be more wonderful than the Prophets since thou wast granted to baptize in the running waters Him Whom thou didst proclaim. Then having endured great suffering for the Truth, thou didst rejoice to bring, even to those in hell, the good tidings that God Who had appeared in the flesh takes away the sin of the world and grants us the great mercy.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Kontakion}
}

\noindent
\justifying
{
\scriptsize
O Prophet of God and Forerunner of Grace, having obtained thy head from the earth as a most sacred rose, we are always receiving healings; for still as of old in the world thou preachest repentance.
}
\medskip

\noindent
\centering
{
\footnotesize
\underline{\textbf{WEDNESDAY \& FRIDAY}}
}
\smallskip

\noindent
\centering
{
\color{red}
\footnotesize
\textit{Commemoration of the Cross \& Passion of our Lord Jesus Christ}
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Troparion}
}

\noindent
\justifying
{
\scriptsize
O Lord, save Thy people and bless Thine inheritance. Grant victory over their enemies to Orthodox Christians, and protect Thy people with Thy Cross.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Kontakion}
}

\noindent
\justifying
{
\scriptsize
O Christ our God, Who wast voluntarily lifted up on the Cross, grant Thy mercies to Thy new people named after Thee. Gladden with Thy power Orthodox Christians and give them victory over their enemies. May they have as an ally that invincible trophy, Thy weapon of peace.
}
\newpage

\noindent
\centering
{
\footnotesize
\underline{\textbf{THURSDAY}}
}
\smallskip

\noindent
\centering
{
\color{red}
\footnotesize
\textit{Commemoration of the Holy Apostles \& St. Nicholas}
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Troparion}
}

\noindent
\justifying
{
\scriptsize
Holy Apostles, intercede with our merciful God, that He may grant to our souls the forgiveness of our sins.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Kontakion to St. Nicholas}
}

\noindent
\justifying
{
\scriptsize
The truth of things revealed thee to thy flock as a rule of faith, a model of meekness, and a teacher of temperance. Therefore thou hast won the heights by humility, riches by poverty. Holy Father Nicholas, intercede with Christ our God that our souls may be saved.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Kontakion to the Holy Apostles}
}

\noindent
\justifying
{
\scriptsize
Thou hast taken the firm and divinely inspired Preachers, O Lord, the top Apostles, for the enjoyment of Thy blessings and for repose. For Thou hast accepted their labours and death as above every burnt offering, O Thou Who alone knowest the secrets of our hearts.
}
\medskip

\noindent
\centering
{
\footnotesize
\underline{\textbf{SATURDAY}}
}
\smallskip

\noindent
\centering
{
\color{red}
\footnotesize
\textit{Commemoration of the Mother of God, all Saints, \& the Faithful Departed}
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Troparion for all Saints}
}

\noindent
\justifying
{
\scriptsize
Apostles, Martyrs, and Prophets, holy Hierarchs, Saints and Righteous, having fought the good fight and kept the faith you have boldness towards the Saviour. Intercede for us with Him, for He is good, we pray, that He may save our souls.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Troparion for the Faithful Departed}
}

\noindent
\justifying
{
\scriptsize
Remember the souls of Thy servants, O Lord, for Thou art good, and insofar as they sinned in this life, forgive them; for no one is sinless but Thee, Who canst also give rest to the departed.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Kontakion for the Faithful Departed}
}

\noindent
\justifying
{
\scriptsize
With the Saints, give rest, O Christ, to the souls of Thy servants, where there is no pain, no sorrow, no sighing, but life everlasting.
}
\smallskip

\noindent
\centering
{
\footnotesize
\textbf{Kontakion for Martyrs}
}

\noindent
\justifying
{
\scriptsize
The world offers to Thee, O Lord, as the Father of creation, the God-bearing Martyrs as the first-fruits of nature. By their prayers through the Mother of God keep Thy Church in deep peace, O Most Merciful One.
}
\bigskip

\centering
{
\color{red}
\textsc{Glory Be to God for All Things!}
}
\medskip

\sectionlinetwo{red}{88}

\end{document}
